---
title: "Linking Code Blocks"
author: "Doug Hemken"
date: "`r format(Sys.Date(), '%b %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Basic Use of Statamarkdown}
  %\VignetteEngine{knitr::rmarkdown_notangle}
  \usepackage[utf8]{inputenc}
---

```{r backtick, echo=FALSE, results="hide"}
backtick <- "`"
```

Each code chunk in your dynamic markdown document runs
as a separate batch file in Stata.  This means that
the results of one code chunk do ***not*** automatically
carry over to the next.  You can have the results of
a chunk carry over to all subsequent chunks by using
the `collectcode=TRUE` chunk option.

Collected code accumulates, and runs silently before each
subsequent chunk.

## Setup Stata Engine
If necessary, also specify the Stata executable location.
```{r stata_setup}
library(Statamarkdown)
```

##An Example
In this example we calculate a new variable in a first
code chunk.  Then in a later code chunk we also use 
the new variable.

###First code block:
In the first code chunk, use the `collectcode` option.

    `r backtick```{r first, collectcode=TRUE}
    sysuse auto, clear
    generate gpm = 1/mpg
    summarize price gpm
    `r backtick```

Which looks like this in your document:
```{r first-Stata, collectcode=TRUE}
sysuse auto, clear
generate gpm = 1/mpg
summarize price gpm
```

##Second code block:
Then you can use the new variable in a later code chunk.

    `r backtick```{r second}
    regress price gpm
    `r backtick```
    
Which looks like this in your document:
```{r second-Stata}
regress price gpm
```

