---
title: "Basic Use of Statamarkdown"
author: "Doug Hemken"
date: "`r format(Sys.Date(), '%b %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Basic Use of Statamarkdown}
  %\VignetteEncoding{UTF-8}
---

This discussion assumes you already have a basic understanding
of Markdown for document formatting, Rmarkdown to include executable
code in a document, and Stata to write the code.

## First attach the `Statamarkdown` library
Your first code chunk will look something like this:

    ```{r library}`r ''`
    library(Statamarkdown)
    stataexe <- find_stata()
    ```
    
This will either report that Stata was found, or
that you need to specify it\'s location yourself.
```{r library}
library(Statamarkdown)
stataexe <- find_stata()
```

You can hide all of this so it does not appear in your
final document by using the `include=FALSE`
chunk options.

## If Stata was not found
You will need to specify this yourself, as an alternative line in
the \"library\" code block.
```{r stataexe, eval=FALSE}
stataexe <- "C:/Program Files/Stata16/StataSE-64.exe"
```

If you do not know where to find you Stata executable (app),
open Stata and issue the command `sysdir`.  The line labeled 
`STATA: ` is the folder where your Stata executable is located. 
You can browse there with your computer\'s file explorer to 
see the actual file name of the Stata executable, which varies
by operating system, Stata version, and Stata flavor.

Then you should set the Stata executable
path as a default chunk option.
```{r enginepath, eval=FALSE}
knitr::opts_chunk$set(engine.path = list(stata = stataexe))
```
## Then set up Stata code chunks.
A simple code chunk in Rmarkdown might look like:

    ```{stata example}`r ''`
    sysuse auto
    summarize
    ```

And in your document this would produce:
```{stata example}
sysuse auto
summarize
```
