---
title: "Combining Stata and R"
author: "Doug Hemken"
date: "`r format(Sys.Date(), '%b %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Combining Stata and R}
  %\VignetteEncoding{UTF-8}
---

One of the virtues of processing your dynamic documents through R
is that you can use more than one programming language in a single
document.  Many of us are multi-lingual, and it is often quicker 
and easier to execute part of a project in one language, while 
completing your work in another.  This is especially common when
you are in the process of learning a new language, or if part of
your work involves a specialized language with limited capabilities.

## Some Setup for Stata
Some initial set up is required to use Stata to process commands. 
You would include an initial fenced code block (\"code chunk\")
to do this.  Use the `echo=FALSE, message=FALSE`
chunk options to hide this from your readers.

````
```{r Statasetup}`r ''`
library(Statamarkdown)
stataexe <- find_stata()
knitr::opts_chunk$set(engine.path = list(stata = stataexe))
```
````

```{r Statasetup, echo=FALSE, message=FALSE}
library(Statamarkdown)
stataexe <- find_stata()
knitr::opts_chunk$set(engine.path = list(stata = stataexe))
```

Then, to switch languages, you just indicate the language in
the code fence.

## Using Stata 

````
```{stata}`r ''`
sysuse auto
regress mpg weight
```
````

```{stata}
sysuse auto
regress mpg weight
```

## Using R

````
```{r cars}`r ''`
summary(lm(mpg ~ wt, data=mtcars))
```
````

```{r cars}
summary(lm(mpg ~ wt, data=mtcars))
```

